Memory for television episodes preserves event content while introducing new across-event similarities

### 2019-09-13 paper/main.tex
Added placeholder precision distinctiveness example figure
updated abstract

%\title{How is experience transformed into memory?}
%\title{A content-based framework for capturing stimulus and memory dynamics reveals event-like structure in naturalistic episodic recall}
%\title{A content-based model characterizing/describing/representing how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
%\title{A content-based framework describing the temporal dynamics of experiences and memories reveals event-like structure in naturalistic episodic recall}
%\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
%\title{Recalling naturalistic experiences exhibits event-like structure}
%\title{A novel framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
\title{A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing}

\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}
Our life experiences unfold over time in highly complex manner, with the evolving presence of numerous intricate features describing our journey between each event we encounter. Here, we propose a framework for mapping dynamic naturalistic episodes onto geometric spaces as \textit{experience trajectories} that capture the temporal dynamics of real-world content. Within this geometric framework, one may compare the shape of the trajectory formed by an experience to that defined by one's later recollection to characterize our memories' recovery and distortion of the external world. Here, we apply this approach to a naturalistic memory experiment in which participants viewed and verbally recounted a video, and find that the video and subsequent recalls share both an experience-specific shape and a discernible event-like structure.  Despite this apparent similarity, we find that the level of \textit{precision} with which individuals recounted various events and the \textit{distinctiveness} of recall for those events were varied and predictive of overall memory performance. Finally, we identify a network of brain structures that is sensitive to the ``shapes" of our ongoing experiences, and an overlapping network sensitive to how we will later remember them.  Our framework and findings underscore the rich event-like structure of the external world and our memories, and offer novel, content-sensitive measures for assessing episodic memory
%Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.  Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.  We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.  We apply this approach to a naturalistic memory experiment which had participants view and recount a video.  We find that the video and subsequent recall share an event-like structure, and that the ``shapes'' of the trajectories formed by participants' recountings were all highly similar to that of the original video. Further, participants' that recounted the events with a high level of precision and in a distinctive way had better subsequent memory performance. Lastly, we identified a network of brain structures that are sensitive to the shapes of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences. These results highlight the rich event-like structure of memories for our life experiences, and introduce a novel framework for mapping between dynamic life experiences and their mnemonic counterparts.
\end{abstract}

@@

@@

%\bibliography{memlab}
\bibliography{/Users/paxtonfitzpatrick/Documents/Dartmouth/CDL/CDL-bibliography/memlab.bib}

>>>>

\title{Memory for television episodes preserves event content while introducing new across-event similarities}

\author{Andrew C. Heusser\textsuperscript{1, 2}, Paxton C. Fitzpatrick\textsuperscript{1}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}
The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.  Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.  We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how experiences are segmented into discrete events, and how the contents of a event sequences evolve over time.  We apply this approach to a naturalistic memory experiment which had participants view and recount a television episode.  The content of participants' recountings of events from the original episode closely matched the original episode's content.  However, the similarity patterns \textit{across} events was much different in the original episode as compared with participants' recountings. We also identified a network of brain structures that are sensitive to the ``shapes'' of ongoing experiences, and an overlapping network that is sensitive (at the time of encoding) to how people later remembered those experiences in relation to other experiences.  In this way, modeling the content of richly structured experiences can reveal how (geometrically and conceptually) those experiences are segmented into events and integrated into our memories of other experiences.
\end{abstract}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/precision_distinctiveness_example}
\caption{\small \textbf{Precision and Distinctiveness Example.}}
\label{fig:precision-distinctiveness-example}
\end{figure}

@@

%\bibliography{memlab}
\bibliography{CDL-bibliography/memlabr}
